The SMT Competition 2015--2018

### 2019-08-31 2018/report/SMT-COMP.tex
Minor

Further, to promote a wide comparison between tools, there was no
restriction on the number of solver versions participants may submit,
e.g., for different competition tracks or with differently tuned
internal components.  Organizers reserved the right to not accept
multiple versions of a solver in case the number of solver submissions
is too large given the computational resources, but in the past four
years, exercising this right was not necessary.
Table~\ref{table:participants-history} shows in more detail how many
versions of each solver were submitted in each year.

>>>>

Further, to promote a wide comparison between tools, there was no
restriction on the number of solver versions participants may submit,
e.g., for different competition tracks or with differently tuned
internal components.  Organizers reserved the right to not accept
multiple versions of a solver in case the number of solver submissions
is too large for the computational resources, but in the past four
years, exercising this right was not necessary.
Table~\ref{table:participants-history} shows in more detail how many
versions of each solver were submitted in each year.
